---
title: "Digit Classification using SVM"
author: "Gowrisankar JG"
date: "24/05/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Loading the dataset
```{r}
letters <- read.csv("letterdata.csv")
str(letters)
```

Dividing data into training and test set
```{r}
letters_train <- letters[1:16000,]
letters_test <- letters[16001:20000,]
```

## Training a model
Kernel specifies a non-linear mapping such as :  
"rbfdot" = radial basis  
"polydot" = polynomial  
"tanhdot" = hyperbolic tangent sigmoid  
"vanilladot" = linear  
```{r}
require(kernlab)
letter_classifier <- ksvm(letter ~ ., data = letters_train, kernel = "vanilladot")

letter_classifier
```

Evaluating model performance
```{r}
letter_predict <- predict(letter_classifier, letters_test)
head(letter_predict)
```

Checking the number of letters correctly predicted
```{r}
match = letter_predict==letters_test$letter
prop.table(table(match))
```

## Improving model performance

Checking the Gaussian RBF kernel performance
```{r}
letter_rbf = ksvm(letter~., data = letters_train, kernel = "rbfdot", C = 100)
letter_rbf_predict = predict(letter_rbf, letters_test)
match = letter_rbf_predict == letters_test$letter
prop.table(table(match))
```
